---
title: "Final Presentation"
author: "Author: Kate Metzger"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # hide all the code
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

I used tidyverse for data manipulation and plotting.

```{r, echo = TRUE}
library(tidyverse)
```

## Data Analyst Job Postings Dataset

I used a dataset from Kaggle, Data Analyst Job Postings [Pay, Skills, Benefits] Center](https://www.kaggle.com/datasets/lukebarousse/data-analyst-job-postings-google-search). This dataset is updated daily and collection started on November 4, 2022.  

##

**Variables in the Dataset:**

* `index`: file original index
* `title`: job title listed in job posting
* `company_name`: the company that listed the job posting
* `location`: city and state
* `via`: social media platform that posted the job listing
* `description`: full description from the job posting  
* `extensions`: common keywords for job postings
* `posted_at`: time posted in reference to `data_time` column
* `schedule_type`: full-time, part-time, or contract type job
* `work_from_home`: True or NaN (blank)

## 

* `search_term`: search term in google to get job posting results
* `date_time`: date and time job pulled from google
* `search_location`: search location in google to get job posting results

I removed columns that were practically empty and removed the word "via" from the `via` column. 

```{r}
data <- read_csv("data/gsearch_jobs.csv")
data <- data[,-1]
data <- separate(data, col = via, into=c('na', 'via'), sep = " ")
data <- select(data, -c("commute_time","salary_pay","salary_rate", "salary_avg", "salary_min", "salary_max", "salary_hourly", "salary_yearly", "salary_standardized", "salary", "job_id", "thumbnail", "na"))
```

##

```{r, fig.align = "center", fig.width = 7.5, fig}
data2 <- data %>%
  filter(via == 'LinkedIn' | via == 'Indeed' | via == 'ZipRecruiter' | via == 'Monster' | via == 'Upwork' | via == 'Adzuna')
ggplot(data2, aes(x = via, fill = via)) + 
  geom_bar(color = 'black') + 
  labs(title = "Most Popular Job Posting Websites", 
       x = "Social Media Platform", 
       y = "Count") +
  theme_bw() +
  theme(legend.position = "none")
```

##

```{r, fig.align = "center"}
data3 <- count(data, work_from_home)

# glimpse(data3)
  
ggplot(data3, aes(x = "", y = work_from_home, fill = work_from_home)) +
  geom_col(color = "black") +
  coord_polar(theta = "y") +
  theme_void() +
  labs(title = "Work From Home Status for Job Listings", 
       fill = "WFH Status", 
       y = "", 
       caption = "NA either means WFH status was not listed or job is worked in office") +
  scale_fill_manual(values = "#CC79A7")
```

##

```{r, fig.align = "center"}
data4 <- data  %>%
  filter(grepl('Health insurance', extensions))

ggplot(data4,  aes(x = schedule_type, fill = schedule_type)) +
  geom_bar() + 
  labs(title = "Type of Job and Which offer Health Insurance",
       x = "Schedule Type",
       y = "Count",
       fill = "Schedule Type") +
  theme_bw()
```